Trends of SDR in Thessaloniki

### 2023-10-19 Article.Rmd
Commit 2023-10-19 18:14

```{r szatrends, echo = FALSE, fig.cap='Distribution of the SDR\'s long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$).', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrends-1.png")
knitr::include_graphics("./images/SzaTrends-4.png" )
knitr::include_graphics("./images/SzaTrends-7.png")
```

@@

```{r echo = FALSE, fig.cap='SDR trend ~ SZA', out.width='100%'}
knitr::include_graphics("./images/SzaTrendsSeasTogether-2.png")
```

>>>>

```{r szatrends, echo = FALSE, fig.cap='*** Daily *** Distribution of the SDR\'s long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$).', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrends-1.png")
knitr::include_graphics("./images/SzaTrends-4.png" )
knitr::include_graphics("./images/SzaTrends-7.png")
```
```{r szatrendsmonthly, echo = FALSE, fig.cap='*** Montlhly *** Distribution of the SDR\'s long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$).', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics("./images/SzaTrendsMonthly-1.png")
knitr::include_graphics("./images/SzaTrendsMonthly-4.png" )
knitr::include_graphics("./images/SzaTrendsMonthly-7.png")
```

@@

```{r echo = FALSE, fig.cap='*** Daily *** SDR trend ~ SZA', out.width='100%'}
knitr::include_graphics("./images/SzaTrendsSeasTogether-2.png")
```

```{r echo = FALSE, fig.cap='*** Montly *** SDR trend ~ SZA', out.width='100%'}
knitr::include_graphics("./images/SzaTrendsSeasTogetherMonthly-2.png")
```
